
% The \section{} command formats and sets the title of this
% section. We'll deal with labels later.
\section{Introduction}
\label{sec:intro}

When given multiple options in a situation with unknown outcomes,
naturally one does not know whether to explore more options or stick
to the best option that one knows. A multi-armed bandit problem
enables us to study the exploration-exploitation trade-off in
reinforcement learning. In this problem, an agent is faced with
multiple ``arms'' (though often the term slot-machine is used), in
which each arm has a reward distribution. The agent's goal is to
determine a policy that informs it which arm to pick at any given
state. Should it pick the arm that it knows to be the most successful
to this point, or should it explore other options in the case that it
can find a better alternative? That is the central question of the
exploration-exploitation trade-off that we would like to answer.

This problem is interesting to Artificial Intelligence researchers due to
the number of interesting practical uses that it has been applied
to. For example, the multi-armed bandit problem has been used to model
clinical trial treatments, ad placement, website optimization, and 
computer game-playing \cite{bubeck}. Furthermore, the idea of
reinforcement learning can summarize most of the field of Artificial
Intelligence: place an agent in an unknown environment, with unknown
rules, and have the agent determine what to do to thrive \cite{aima}.

The multi-armed bandit problem has been analyzed extensively by
\cite{auer}, and this paper attempts to reproduce a subset of their
work. The remainder of this paper includes background information on
reinforcement learning and the multi-armed bandit problem, the
experiments we performed, the results, and finally our conclusions.


% In this section, you should introduce the reader to the problem you
% are attempting to solve. For example, for the first project: describe
% the $15$-puzzle, and why it's interesting as an A.I. problem. You
% should also cite and briefly describe other related papers that have
% tackled this problem in the past --- things that came up during the
% course of your research. In the AAAI style, citations look like
% \cite{aima} (see the comments in the source file \texttt{intro.tex} to
% see how this citation was produced). Conclude by summarizing how the
% remainder of the paper is organized.\\

% Citations: As you can see above, you create a citation by using the
% \cite{} command. Inside the braces, you provide a "key" that is
% uniue to the paper/book/resource you are citing. How do you
% associate a key with a specific paper? You do so in a separate bib
% file --- for this document, the bib file is called
% project1.bib. Open that file to continue reading...

% Note that merely hitting the "return" key will not start a new line
% in LaTeX. To break a line, you need to end it with \\. To begin a 
% new paragraph, end a line with \\, leave a blank
% line, and then start the next line (like in this example).
% Overall, the aim in this section is context-setting: what is the
% big-picture surrounding the problem you are tackling here?

